Recursive algorithms and branching for nonmaximal embeddings

### 2010-11-23 AffineLieAlgebras/InformalNotes/article.tex
Some work with pictures
New changes from V.D.

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras
  integrable highest weight modules are studied. The decomposition algorithm
  based on the injection fan technique is developed for the case of reductive
  subalgebra. In particular we consider the situations where
  the Weyl denominator becomes singular with respect to the subalgebra.
  We study the modifications of the injection fan technique and demonstrate
  that for any reductive subalgebra it is possible to define the
  injection fan -- the tool that describes
  explicitly the recurrent properties of branching coefficients.
  Possible applications of subtracted fans in CFT models are considered.
\end{abstract}
\ams{17B67, 17B10}
\submitto{\JPA}
%\maketitle

@@

Usually only the maximal reductive subalgebras $\frak{a} \subset \frak{g} $ are considered since the case of non-maximal subalgebra
can be obtained using the chain of maximal injections. In this paper we find out that the recurrent properties
for branching coefficients can be explicitly formulated for an arbitrary reductive subalgebra.
The principal point is to consider the subalgebra $\af$ together with its
counterpart $\afb$ "orthogonal" to $\af$ with respect to the Killing form.
For any reductive $\af$ the subalgebra $\afb \subset \frak{g} $ is a regular and reductive.
For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
$\left(  \af, \afb \right)$ we consider
%In the the group algebra $\mathcal{E}\left( \frak{g} \right)$ we consider
the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
in the Weyl character formula
$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite{humphreys1997introduction})
the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
$\left(  \af, \afb \right)$ the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
This decomposition provides the possibility to construct the recurrent property for the branching coefficients corresponding
to the injection $\frak{a} \longrightarrow \frak{g} $.
This property is formulated in
terms of a specific element of the group algebra $\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
Using this tool we formulate a simple and
explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or non-maximal)
subalgebras of finite-dimensional and affine Lie algebras.
In the case of maximal embedding the corresponding fan becomes unsubtracted and the recurrent relations described
earlier in \cite{ilyin812pbc} are reobtained.

@@

The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the general notations.
In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula for
the subtracted recurrent formula for anomalous
branching coefficients and describe the decomposition algorithm for integrable highest weight modules
$L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
(subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several
simple examples for finite-dimensional Lie algebras. The affine Lie algebras and their applications in
CFT models are considered in Section \ref{sec:phys-appl}.
Possible further developments are discussed (Section \ref{sec:conclusion}).

@@

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}\quad $
$\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
\left( \alpha \right) }}\right) $--- the
denominator.

@@

In the Weyl-Kac formula both numerator and denominator  can be considered
as formal elements containing the singular weights of the Verma modules $V^{\xi}$
with the highest weights $\xi=\mu$ and $\xi=0$ \cite{humphreys1997introduction}.
We attribute singular numerators to the corresponding integrable modules $L^{\mu }$
and $L_{\af}^{\nu }$:
\begin{equation*}
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho },
\end{equation*}
\begin{equation*}
\Psi _{ \af}^{\left( \nu \right) }:=
\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w\circ (\nu +\rho
_{_{\af}})-\rho _{_{\af}}}.
\end{equation*}
and use the Weyl-Kac formula in the form
\begin{equation}
\label{Weyl-Kac2}
ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}
{\Psi ^{\left( 0 \right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
\end{equation}

@@

Consider the root subspace
$\frak{h}_{\perp \af}^{\ast }$ orthogonal to the roots in $\Delta _{\af}$,
\begin{equation*}
\frak{h}_{\perp \af}^{\ast }=:\left\{ \eta \in \frak{h}^{\ast }
|\forall \alpha \in \Delta _{\af};\alpha \bot \eta \right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\Delta _{\af}$,
\begin{eqnarray*}
\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
\alpha \in \Delta _{\af};\alpha \bot \beta \right\} , \\
\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall \alpha ^{+}\in \Delta _{\af}^{+};\alpha ^{+}\bot \beta
^{+}\right\} .
\end{eqnarray*}
Let $W_{\af_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\af%
_{\perp }}^{+}$ . The subsystem $\Delta _{\af_{\perp }}$ determines the
subalgebra $\af_{\perp }$ with the Cartan subalgebra $\frak{h}_{\af%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
}|\forall \alpha \in \Delta _{\af}\cup \Delta _{\af_{\perp
}};\alpha \bot \eta \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
\end{eqnarray*}
Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
$\left( \af,\af_{\perp}\right) $
of subalgebras in $\frak{g}$.

@@

To describe the recurrent properties for branching coefficients $b_{\nu
}^{(\mu )}$ we shall use the technique elaborated in \cite{ilyin812pbc}. One of the
main tools is the set of weights $\Gamma _{\af\subset \frak{g}%
} $ called the injection fan. As far as we consider more general situation
(where the injection is not maximal) the notion of the injection fan is
modified:

\begin{definition}
\label{fan-definition} For the product
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
)e^{-\gamma }  \label{eq:6}
\end{equation}
consider the carrier $\Phi _{\af\subset \frak{g}}\subset P_{\af}$
of the function $s(\gamma )=\det \left( \gamma \right) $ :
\begin{equation}
\Phi _{\af\subset \frak{g}}=\left\{ \gamma \in P_{\af}|s(\gamma
)\neq 0\right\}   \label{eq:37}
\end{equation}
The ordering of roots in $\co{\Delta _{\af}}$ induce the
natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
\begin{equation}
\Gamma _{\af\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.
\end{definition}
In the next subsection we shall see how the injection fan defines the recurrent
properties of branching coefficients. It must be noticed that the injection fan is
the universal instrument that depend only on the injection.

@@

\begin{proof}
With $u\in U $   and $v\in W_{\afb}$ perform the decomposition
\begin{equation*}
u(\mu +\rho )=\pi _{\left( \af\right) } u(\mu +\rho )+\pi _{\left(
\widetilde{\af_{\perp }}\right) } u(\mu +\rho )
\end{equation*}
for the singular weight $vu(\mu +\rho )-\rho$:
\begin{equation}
\label{sing-decomp-1}
\begin{array}{lcl}
vu(\mu +\rho )-\rho &=&\pi _{\left( \af\right) }\left( u(\mu +\rho
)\right) -\rho +\rho _{\af_{\perp }}+\pi _{\left( \hfb\right) }\rho \\
&& + \ v\left( \pi _{\left( \widetilde{%
\af_{\perp }}\right) }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
\af_{\perp }}\right) -\rho _{\af_{\perp }} -\pi _{\left( \hfb\right) }\rho.
\end{array}
\end{equation}
Use the defect $\mathcal{D}_{\afb}$ (\ref{defect-perp}) to simplify
the first summand in (\ref{sing-decomp-1}):
\begin{equation*}
\begin{array}{r}
\pi _{\left( \af\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
\mathfrak{a}_{\perp }}+\pi _{\left( \hfb\right) }\rho = \\
\pi _{\left( \af\right) }\left( u(\mu +\rho )\right) -\pi _{\af}\rho
-\pi _{\afb}\rho +\rho _{\afb}= \\
\pi _{\left( \af\right) }\left( u(\mu +\rho )-\rho \right) +%
\mathcal{D}_{\afb},
\end{array}
\end{equation*}
and the second one:
\begin{equation*}
\begin{array}{c}
v\left( \pi _{\left( \widetilde{%
\af_{\perp }}\right) }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
\af_{\perp }}\right) -\rho _{\af_{\perp }}-\pi _{\left( \hfb\right) }\rho=\\
v\left( \pi _{\left( \widetilde{%
\afb}\right) }u(\mu +\rho )
- \mathcal{D}_{\afb} - \pi _{\left( \afb\right) }\rho-\pi _{\left( \hfb\right) }\rho
+\rho _{\afb}\right) -\rho _{\afb}=\\
v\left( \pi _{\left( \widetilde{%
\afb}\right) }\left[ u(\mu +\rho )-\rho\right]
- \mathcal{D}_{\afb}
+\rho _{\afb}\right) -\rho _{\afb}.
\end{array}
\end{equation*}
These expressions provide a kind of a factorization in the anomalous element $\Psi^{\mu
}$ and we find in it the combination of
anomalous elements $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ of the
subalgebra $\widetilde{\af_{\perp }}$-modules $L_{\widetilde{\af%
_{\perp }}}^{\eta }$:
\begin{equation*}
\begin{array}{l}
\Psi^{\mu }=\sum_{u\in U}\sum_{v\in W_{\af_{\perp }}}
\epsilon (v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
=\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]
+\mathcal{D}_{\af_{\perp }}}\sum_{v\in W_{\af_{\perp }}}\epsilon
(v)e^{v\left( \pi _{\left( \widetilde{\af_{\perp }}\right) }\left[
u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}+\rho _{\af%
_{\perp }}\right) -\rho _{\af_{\perp }}}= \\
=\sum_{u\in U}\;\epsilon (u)e^{\pi _{\left( \af\right) }\left[ u(\mu
+\rho )-\rho \right] +\mathcal{D}_{\af_{\perp }}}\Psi _{\widetilde{%
\af_{\perp }}}^{\pi _{\left( \widetilde{\af_{\perp }}\right) }%
\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}}
\end{array}
\end{equation*}

@@

\item  Select the positive roots $\alpha \in \Delta ^{+}$ orthogonal to the
roots in $\Delta _{\af}$ i.e. form the set $\Delta _{\bot }^{+}$.

@@

\item  Select the weights $\left\{ \mu _{\widetilde{\af_{\perp }}%
}\left( w\right) =\pi _{\widetilde{\af_{\perp }}}\left[ w(\mu +\rho
)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
\af_{\perp }}}}\right\} $. Since the set $\Delta _{\bot }^{+}$ is fixed
we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
\af_{\perp }}}}$ (by computing its scalar product with the roots from $%
\Delta _{\bot }^{+}$).

\item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
calculate the dimensions of the corresponding modules $\mathrm{\dim }\left(
L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
}\left( u\right) }\right) $.

@@

\begin{figure}[p]
  \noindent\centering{
    \includegraphics[width=80mm]{figure1.eps}
  }
  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
    The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is shown by the black vector.
    The superscripts of the highest weights
  $\af_{\perp }^{\mu_{\af_{\perp }}}\left( u\right)$ are the products $\epsilon(w)\dim\left(L_{\af_{\perp }}^{\mu
_{\af_{\perp }}\left( u\right) }\right)$
    The weights of the singular element $\Psi^{(\omega_1)}$ are marked by circles with superscripts indicating
    the corresponding determinants $\epsilon(w)$.}
  \label{fig:B2_A1}

%\end{figure}
%\begin{figure}[pb]
  \noindent\centering{
    \includegraphics[width=80mm]{figure2.eps}
  }
  \caption{Here in addition to the diagram presented above (Figure(\ref{fig:B2_A1}))
  the weights of $\afb=A_1$-modules $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$
  originating in the points $\pi _{\af}\left[ u(\mu +\rho )-\rho \right] $
are shown by dotted lines.
    The superscripts over the highest weights  $\mu_{\af_{\perp }}\left( u\right)$
    are now the products $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.
    Coordinates along the root $\beta$ are counted in terms of the fundamental weight of $\af$. }
\label{fig:B2_A1_2}
\end{figure}

>>>>

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras
  integrable highest weight modules are studied. The decomposition algorithm
  based on the injection fan technique is developed for the case of an arbitrary
  reductive subalgebra. In particular we consider the situation where
  the Weyl denominator becomes singular with respect to the subalgebra.
  We study the modifications of the fan technique and demonstrate
  that for any reductive subalgebra it is possible to define the
  injection fan -- the tool that describes
  explicitly the recurrent properties of branching coefficients.
  Possible applications of fan technique in CFT models are considered.
\end{abstract}
\ams{17B67, 17B10}
\submitto{\JPA}
%\maketitle

@@

Usually only maximal reductive subalgebras $\frak{a} \subset \frak{g} $ are considered since the case of non-maximal subalgebra
can be obtained using the chain of maximal injections. In this paper we find out that the recurrent properties
for branching coefficients can be explicitly formulated for an arbitrary reductive subalgebra.
The principal point is to consider the subalgebra $\af$ together with its
counterpart $\afb$ "orthogonal" to $\af$ with respect to the Killing form.
For any reductive algebra $\af$ the subalgebra $\afb \subset \frak{g} $ is regular and reductive.
For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
$\left(  \af, \afb \right)$ we consider
%In the the group algebra $\mathcal{E}\left( \frak{g} \right)$ we consider
the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
in the Weyl character formula
$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite{humphreys1997introduction})
the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair
$\left(  \af, \afb \right)$ the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
This decomposition provides the possibility to construct the recurrent property for branching coefficients corresponding
to the injection $\frak{a} \longrightarrow \frak{g} $.
This property is formulated in
terms of a specific element of the group algebra $\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
Using this tool we formulate a simple and
explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
subalgebras of finite-dimensional and affine Lie algebras.
In the case of maximal embedding the corresponding fan becomes unsubtracted and the recurrent relations described
earlier in \cite{ilyin812pbc} are reobtained.

@@

The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the general notations.
In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula based on
recurrent properties of anomalous branching coefficients and describe the decomposition algorithm
for integrable highest weight modules
$L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
(subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several
simple examples for finite-dimensional Lie algebras. The affine Lie algebras and their applications in
CFT models are considered in Section \ref{sec:phys-appl}.
Possible further developments are discussed (Section \ref{sec:conclusion}).

@@

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}\quad $
$\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
\left( \alpha \right) }}\right) $--- the Weyl denominator.

@@

In the Weyl-Kac formula both numerator and denominator  can be considered
as formal elements containing the singular weights of the Verma modules $V^{\xi}$
with the highest weights $\xi=\mu$ and $\xi=0$ \cite{humphreys1997introduction}.
We attribute singular elements to the corresponding integrable modules $L^{\mu }$
and $L_{\af}^{\nu }$:
\begin{equation*}
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho },
\end{equation*}
\begin{equation*}
\Psi _{ \af}^{\left( \nu \right) }:=
\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w\circ (\nu +\rho
_{_{\af}})-\rho _{_{\af}}}.
\end{equation*}
and use the Weyl-Kac formula in the form
\begin{equation}
\label{Weyl-Kac2}
ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}
{\Psi ^{\left( 0 \right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
\end{equation}

@@

Consider the root subspace
$\frak{h}_{\perp \af}^{\ast }$ orthogonal to  $\af$,
\begin{equation*}
\frak{h}_{\perp \af}^{\ast }=:\left\{ \eta \in \frak{h}^{\ast }
|\forall h \in \hf_{\af};  \eta\left(h \right)=0 \right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\af$,
\begin{eqnarray*}
\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|
\forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\} , \\
\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall h \in \hf_{\af};  \beta^{+}\left(h \right)=0  \right\} .
\end{eqnarray*}
Let $W_{\af_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\af%
_{\perp }}^{+}$ . The subsystem $\Delta _{\af_{\perp }}$ determines the
subalgebra $\af_{\perp }$ with the Cartan subalgebra $\frak{h}_{\af%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
}|\forall h \in \hf_{\af\oplus \af_{\perp}}; \eta \left( h \right)=0 \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
\end{eqnarray*}
Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
$\left( \af,\af_{\perp}\right) $
of subalgebras in $\frak{g}$.

@@

To describe the recurrent properties for branching coefficients $b_{\nu
}^{(\mu )}$ we shall use the technique elaborated in \cite{ilyin812pbc}. One of the
main tools is the set of weights $\Gamma _{\af\rightarrow \frak{g}%
} $ called the injection fan. As far as we consider the general situation
(where the injection is not necessarily maximal) the notion of the injection fan is
modified:

\begin{definition}
\label{fan-definition} For the product
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
)e^{-\gamma }  \label{eq:6}
\end{equation}
consider the carrier $\Phi _{\af\subset \frak{g}}\subset P_{\af}$
of the function $s(\gamma )=\det \left( \gamma \right) $ :
\begin{equation}
\Phi _{\af\subset \frak{g}}=\left\{ \gamma \in P_{\af}|s(\gamma
)\neq 0\right\}   \label{eq:37}
\end{equation}
The ordering of roots in $\co{\Delta _{\af}}$ induce the
natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
\begin{equation}
\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.
\end{definition}
In the next subsection we shall see how the injection fan defines the recurrent
properties of branching coefficients. It must be noticed that the injection fan is
the universal instrument that depend only on the injection.

@@

\begin{proof}
With $u\in U $   and $v\in W_{\afb}$ perform the decomposition
\begin{equation*}
u(\mu +\rho )=\pi _{\left( \af\right) } u(\mu +\rho )+\pi _{\left(
\widetilde{\af_{\perp }}\right) } u(\mu +\rho )
\end{equation*}
for the singular weight $vu(\mu +\rho )-\rho$:
\begin{equation}
\label{sing-decomp-1}
\begin{array}{lcl}
vu(\mu +\rho )-\rho &=&\pi _{\left( \af\right) }\left( u(\mu +\rho
)\right) -\rho +\rho _{\af_{\perp }}+\pi _{\left( \hfb\right) }\rho \\
&& + \ v\left( \pi _{\left( \widetilde{%
\af_{\perp }}\right) }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
\af_{\perp }}\right) -\rho _{\af_{\perp }} -\pi _{\left( \hfb\right) }\rho.
\end{array}
\end{equation}
Use the defect $\mathcal{D}_{\afb}$ (\ref{defect-perp}) to simplify
the first summand in (\ref{sing-decomp-1}):
\begin{equation*}
\begin{array}{r}
\pi _{\left( \af\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
\mathfrak{a}_{\perp }}+\pi _{\left( \hfb\right) }\rho = \\
\pi _{\left( \af\right) }\left( u(\mu +\rho )\right) -\pi _{\af}\rho
-\pi _{\afb}\rho +\rho _{\afb}= \\
=\pi _{\left( \af\right) }\left( u(\mu +\rho )-\rho \right) +%
\mathcal{D}_{\afb},
\end{array}
\end{equation*}
and the second one:
\begin{equation*}
\begin{array}{c}
v\left( \pi _{\left( \widetilde{%
\af_{\perp }}\right) }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
\af_{\perp }}\right) -\rho _{\af_{\perp }}-\pi _{\left( \hfb\right) }\rho=\\
v\left( \pi _{\left( \widetilde{%
\afb}\right) }u(\mu +\rho )
- \mathcal{D}_{\afb} - \pi _{\left( \afb\right) }\rho-\pi _{\left( \hfb\right) }\rho
+\rho _{\afb}\right) -\rho _{\afb}=\\
=v\left( \pi _{\left( \widetilde{%
\afb}\right) }\left[ u(\mu +\rho )-\rho\right]
- \mathcal{D}_{\afb}
+\rho _{\afb}\right) -\rho _{\afb}.
\end{array}
\end{equation*}
These expressions provide a kind of a factorization in the anomalous element $\Psi^{\mu
}$ and we find in it the combination of
anomalous elements $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ of the
subalgebra $\widetilde{\af_{\perp }}$-modules $L_{\widetilde{\af%
_{\perp }}}^{\eta }$:
\begin{equation*}
\begin{array}{l}
\Psi^{\mu }=\sum_{u\in U}\sum_{v\in W_{\af_{\perp }}}
\epsilon (v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
=\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]
+\mathcal{D}_{\af_{\perp }}}\sum_{v\in W_{\af_{\perp }}}\epsilon
(v)e^{v\left( \pi _{\left( \widetilde{\af_{\perp }}\right) }\left[
u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}+\rho _{\af%
_{\perp }}\right) -\rho _{\af_{\perp }}}= \\
=\sum_{u\in U}\;\epsilon (u)e^{\pi _{\left( \af\right) }\left[ u(\mu
+\rho )-\rho \right] +\mathcal{D}_{\af_{\perp }}}\Psi _{\widetilde{%
\af_{\perp }}}^{\pi _{\left( \widetilde{\af_{\perp }}\right) }%
\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}}
\end{array}
\end{equation*}

@@

\item  Select the positive roots $\alpha \in \Delta ^{+}$ orthogonal
to  $\af$, i.e. form the set $\Delta _{\bot }^{+}$.

@@

\item  Select the weights $\left\{ \mu _{\widetilde{\af_{\perp }}%
}\left( w\right) =\pi _{\widetilde{\af_{\perp }}}\left[ w(\mu +\rho
)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
\af_{\perp }}}}\right\} $. Since the set $\Delta _{\bot }^{+}$ is fixed
we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
\af_{\perp }}}}$ (by computing its scalar product with the fundamental
weights of $\afb^{+}$).

\item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
calculate the dimensions of the corresponding modules $\mathrm{\dim }\left(
L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
}\left( u\right) }\right) $ using the Weyl dimension formula.

@@

\begin{figure}[p]
  \noindent\centering{
    \includegraphics[width=80mm]{figure1.eps}
  }
  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
    The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is shown by the black vector.
    The weights of the singular element $\Psi^{(\omega_1)}$ are marked by circles with superscripts indicating
    the corresponding determinants $\epsilon(w)$.}
  \label{fig:B2_A1}

%\end{figure}
%\begin{figure}[pb]
  \noindent\centering{
    \includegraphics[width=80mm]{figure2.eps}
  }
  \caption{Here in addition to the diagram presented above (Figure(\ref{fig:B2_A1}))
  the weights of $\left( \afb=A_1 \right)$-modules $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$
  originating in the points $\pi _{\af}\left[ u(\mu +\rho )-\rho \right] $
are shown by dotted lines.
    The superscripts over the highest weights  $\mu_{\af_{\perp }}\left( u\right)$
    are now the products $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.
    Coordinates along the root $\beta$ are counted in terms of the fundamental weight of $\af$. }
\label{fig:B2_A1_2}
\end{figure}

Let's perform the reduction of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$
($\omega_1$ -- the black vector in Figure \ref{fig:B2_A1}). The root $\alpha_1$ is orthogonal to $\beta$,
so we have $\Delta_{\perp}^+ = \left\{ \alpha_1 \right\}$.
According to the definition (\ref{fan-definition})
the fan $\Gamma_{A_1\to B_2}$ consists of two weights:
\begin{equation*}
  \label{eq:22}
  \Gamma_{A_1\to B_2}=\left\{ (1;2),\; (2;-1) \right\},
\end{equation*}
where the second component is the value of the sign function $s(\gamma)$.
The singular weights  $\left\{ w (\omega_1 +\rho)-\rho ;\;w \in W\right\}$
are indicated by circles with the superscript $\epsilon\left( w \right)$.
The space $U$ is the factor $W/W_{\afb}$ where $W_{\afb}=\left\{e,w_1\right\}$.
This means that the singular weights located above the line generated by $\beta$
belong to the Weyl chamber $\overline{C_{\widetilde{\af_{\perp }}}}$.
According to formula (\ref{defect-perp}) in our case we have $\mathcal{D}_{\af_{\perp }}=0$ and
$\hf_{\perp }=0$, thus $\left\{ \mu _{\af_{\perp }}\left( w\right)
=\pi _{\af_{\perp }}\left[ w(\mu +\rho)-\rho \right]\right\}$.
We obtain four highest weights for $\af_{\perp }$-modules. In terms of
$\af_{\perp }$-fundamental weight $\frac{1}{2} \alpha_1$ these highest weights
$\left\{ \mu _{\af_{\perp }}\left( u\right)
=\pi _{\af_{\perp }}\left[ u(\mu +\rho)-\rho \right]| u \in U \right\}$
 are
$\left\{ \left( 1\right) \left( 2\right) \left( 2\right) \left( 1\right) \right\}$. To
visualize the procedure we indicate explicitly in Figure (\ref{fig:B2_A1_2}) how the
corresponding weight diagrams
$\left\{ \mathcal{N}_{\af_{\perp }}^{\mu _{\af_{\perp }}\left( u\right) }\right\} $
are attached to the set of $\af$-weights
$\left\{ \mu _{\af}\left( u\right)\right\} =\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]\right\}
=\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$.
In fact we do not need the
weight diagrams but only the dimensions of the corresponding modules
$L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$ multiplied by
$\epsilon \left( u\right) $. The obtained values are to be placed in $P_{\af}$ at the points
$\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$ to
produce the set of singular weights with anomalous multiplicities:
\begin{equation}
  \label{eq:25}
  \left\{(1;2),\; (0;-3),\; (-4;3),\; (-5;-2)\right\}.
\end{equation}
According to the defenition (\ref{fan-definition})
the fan $\Gamma_{A_1\to B_2}$ consists of two weights:
\begin{equation*}
  \label{eq:22}
  \Gamma_{A_1\to B_2}=\left\{ (1;2),\; (2;-1) \right\},
\end{equation*}
where the second component of the weight is the value of the sign function $s(\gamma)$.
